Motional Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-08-14 sm.tex
Cite steck

\section{Raman Sideband Cooling Pulse Parameters and Sequence}
Here, we list the full Raman sideband cooling (RSC) pulse  parameters and  sequence used to obtain the result in [our paper]. A step of RSC contains a Raman pulse and an optical pumping pulse. The full RSC sequence includes about 1000 pulses in 100 ms.

@@

\subsection{Raman pulse parameters}
Each Raman pulse in the cooling sequence is followed immediately by an optical pumping
pulse.
The full parameters  for the Raman pulses, including the cooling ``axis'', the sideband ``order ($\Delta n$)'', the cooling frequency ``$\delta '$", the carrier ($\Delta n=0$) frequency ``$\delta_0'$'', the pulse ``duration'', the pulse strength in ``full Rabi frequency'', and the beam of which a non-uniform ``power ramp'' is applied,   are  listed in 9 groups below.
The applied cooling frequency, $\delta'$,  is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
of $1.7716261288(10)$GHz[cite].
%All of the relative detunings are negative indicating that the frequency difference is smaller than the zero-field hyperfine splitting. Higher-order sidebands for cooling
%A more negative number corresponds to lower order cooling sidebands
%and a more negative number corresponds to higher order ones.
Due to the Stark shifts of the Raman beams, the carrier  transition, $\delta'_0$, varies with the power of the Raman beams. $\delta'_0$ is given also relative to the zero-field  hyperfine splitting.
The strength of the pulses given in ``Full Rabi frequency'' is the measured two-photon Rabi frequency $\Omega$ divided by the wave function overlap for each order of cooling. The difference between $\delta'$ and $\delta'_0$ gives the motional sideband frequency, $\delta$.
%The full Rabi frequency is given as the two-photon Rabi frequency $\Omega$ including only electronic dipole matrix element excluding the matrix element
%from wavefunction overlap.
Many Raman pulses include a ``power ramp'' with a Blackman envelope~\cite{Kasevich1992} to minimize off-resonant excitations.
Because each Raman pulse is a product of two spatial- and temporal-overlapped laser beams, the ``power ramp'' is applied only to one of the beams for simplicity (we label the beam by the corresponding $F$ number) while the other beam has  a square-pulse shape.
For a Raman pulse with a power ramp,
the full Rabi frequency gives the arithmetics mean over the duration of the pulse.

>>>>

\section{Raman Sideband Cooling Pulse Parameters and Sequence}
Here, we list the full Raman sideband cooling (RSC) pulse parameters and sequence used to obtain the result in our paper.
A step of RSC contains a Raman pulse and an optical pumping pulse.
The full RSC sequence includes about 1000 pulses in 100 ms.

@@

\subsection{Raman pulse parameters}
Each Raman pulse in the cooling sequence is followed immediately by an optical pumping
pulse.
The full parameters for the Raman pulses, including the cooling ``axis'', the sideband ``order ($\Delta n$)'', the cooling frequency ``$\delta '$", the carrier ($\Delta n=0$) frequency ``$\delta_0'$'', the pulse ``duration'', the pulse strength in ``full Rabi frequency'', and the beam of which a non-uniform ``power ramp'' is applied,   are listed in 9 groups below.
The applied cooling frequency, $\delta'$,  is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
of $1.7716261288(10)$GHz\cite{SteckNa}.
%All of the relative detunings are negative indicating that the frequency difference is smaller than the zero-field hyperfine splitting. Higher-order sidebands for cooling
%A more negative number corresponds to lower order cooling sidebands
%and a more negative number corresponds to higher order ones.
Due to the Stark shifts of the Raman beams, the carrier transition, $\delta'_0$, varies with the power of the Raman beams. $\delta'_0$ is given also relative to the zero-field hyperfine splitting.
The strength of the pulses given in ``Full Rabi frequency'' is the measured two-photon Rabi frequency $\Omega$ divided by the wave function overlap for each order of cooling. The difference between $\delta'$ and $\delta'_0$ gives the motional sideband frequency, $\delta$.
%The full Rabi frequency is given as the two-photon Rabi frequency $\Omega$ including only electronic dipole matrix element excluding the matrix element
%from wavefunction overlap.
Many Raman pulses include a ``power ramp'' with a Blackman envelope~\cite{Kasevich1992} to minimize off-resonant excitations.
Because each Raman pulse is a product of two spatial- and temporal-overlapped laser beams, the ``power ramp'' is applied only to one of the beams for simplicity (we label the beam by the corresponding $F$ number) while the other beam has a square-pulse shape.
For a Raman pulse with a power ramp,
the full Rabi frequency gives the arithmetics mean over the duration of the pulse.
